---
title: "`modelsummary` for advanced users"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(modelsummary)
```

# Adding new models

`modelsummary` relies on two functions from the `broom` package to extract model information: `tidy` and `glance`. If `broom` doesn't support the type of model you are trying to summarize, `modelsummary` won't support it out of the box. Thankfully, it is extremely easy to add support for most models using custom methods.

For example, models produced by the `MCMCglmm` package are not currently supported by `broom`. To add support, you simply need to create a `tidy` and a `glance` method:

```r
# load packages and data
library(modelsummary)
library(MCMCglmm)
data(PlodiaPO)

# add custom functions to extract estimates (tidy) and goodness-of-fit (glance) information
tidy.MCMCglmm <- function(object, ...) {
    s <- summary(object, ...)
    ret <- tibble::tibble(term = row.names(s$solutions),
                          estimate = s$solutions[, 1],
                          conf.low = s$solutions[, 2],
                          conf.high = s$solutions[, 3])
    ret
}
glance.MCMCglmm <- function(object, ...) {
    ret <- tibble::tibble(dic = object$DIC,
                          n = nrow(object$X))
    ret
}

# estimate a simple model
model <- MCMCglmm(PO ~ 1 + plate, random = ~ FSfamily, data = PlodiaPO, verbose=FALSE, pr=TRUE)

# summarize the model
msummary(model, statistic = 'conf.int')
```

Two important things to note. First, the methods are named `tidy.MCMCglmm` and `glance.MCMCglmm` because the model object I am trying to summarize is of class `MCMCglmm`. You can find the class of a model by running: `class(model)`.

Second, in the example above, we used the `statistic = 'conf.int'` argument. This is because the `tidy` method produces `conf.low` and `conf.high` columns. In most cases, users will define `std.error` column in their custom `tidy` methods, so the `statistic` argument will need to be adjusted.

If you create new `tidy` and `glance` methods, please consider contributing them to `broom` so that the rest of the community can benefit from your work: https://github.com/tidymodels/broom

# Customizing existing models

The set of available statistics for any given model is determined by the output of the `broom::glance` function. Sometimes, you want to include information that is not included in `glance` output. For instance, you may want to display whether certain regression models include "fixed effects". 

One way to circumvent the limitations of glance is to create a custom method for your models. To illustrate, we load the `lfe` package, which provides the `felm` function to estimate linear regression models with fixed effects. Then, we simulate some data:

```{r, message=FALSE}
library(lfe)
library(broom)
library(modelsummary)

x <- rnorm(1000)
x2 <- rnorm(length(x))
id <- factor(sample(20,length(x),replace=TRUE))
firm <- factor(sample(13,length(x),replace=TRUE))
id.eff <- rnorm(nlevels(id))
firm.eff <- rnorm(nlevels(firm))
u <- rnorm(length(x))
y <- x + 0.5*x2 + id.eff[id] + firm.eff[firm] + u
```

The models produced by `felm` store the names of fixed effects in an object called "fe". For example, if `x` is your models, then `x$fe` will be a character vector with the names of all your fixed effects variables.

We create a custom `glance` method that extracts this information and returns it alongside the regular `glance` output:

```{r}
glance.felm_custom <- function(x, ...) {
    out <- broom:::glance.felm(x, ...)
    for (fe in names(x$fe)) {
        out[[paste('Fixed effects:', fe)]] <- 'X'
    }
    out
}
```

Then, we create a function to fit our models. This function passes all its arguments forward to `felm` using ellipses (`...`). Then, it assigns a new class name. This tells `modelsummary` that it should extract fixed effects names:

```{r}
felm_custom <- function(...) {
    out <- felm(...)
    class(out) <- c('felm_custom', class(out))
    out
}
```

Finally, we fit models and print the table:

```{r}
mod <- list()
mod[[1]] <- lm(y ~ x + x2)
mod[[2]] <- felm_custom(y ~ x + x2 | id)
mod[[3]] <- felm_custom(y ~ x + x2 | firm)
mod[[4]] <- felm_custom(y ~ x + x2 | id + firm)

msummary(mod)
```

# Raw data

The `gt` package allows a bunch more customization and styling. Power users can use `modelsummary`'s `extract` function to produce a tibble which can easily be fed into `gt`.

```r
> modelsummary::extract(models)
# A tibble: 21 x 8
   group     term        statistic `OLS 1` `NBin 1` `OLS 2` `NBin 2` `Logit 1`
   <chr>     <chr>       <chr>     <chr>   <chr>    <chr>   <chr>    <chr>
 1 estimates (Intercept) estimate  64.114  4.218    57.331  4.384    1.006
 2 estimates (Intercept) statistic (5.247) (0.144)  (8.315) (0.233)  (0.710)
 3 estimates Crime_prop  estimate  -0.002  -0.000   -0.002  -0.000   -0.000
 4 estimates Crime_prop  statistic (0.001) (0.000)  (0.001) (0.000)  (0.000)
 5 estimates Infants     estimate  -0.001  ""       0.000   ""       -0.000
 6 estimates Infants     statistic (0.000) ""       (0.000) ""       (0.000)
 7 estimates Donations   estimate  ""      -0.000   ""      -0.000   ""
 8 estimates Donations   statistic ""      (0.000)  ""      (0.000)  ""
 9 gof       R2          ""        0.237   ""       0.073   ""       ""
10 gof       Adj.R2      ""        0.218   ""       0.051   ""       ""
# … with 11 more rows
```

# Multiple imputation results

`modelsummary` can pool and display analyses on several datasets imputed using the `mice` or `Amelia` packages. In this example, we use convenience functions from the `mitools` package to format our data: 

```{r}
library(modelsummary)
library(mitools)
suppressMessages(library(mice))
suppressMessages(library(Amelia))

# Download data from `Rdatasets`
url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url)[, c('Clergy', 'Commerce', 'Literacy')]

# Insert missing values
dat$Clergy[sample(1:nrow(dat), 10)] <- NA
dat$Commerce[sample(1:nrow(dat), 10)] <- NA
dat$Literacy[sample(1:nrow(dat), 10)] <- NA

# Impute with `mice` and `Amelia`
dat_mice <- mice(dat, m = 5, printFlag = FALSE)
dat_amelia <- amelia(dat, m = 5, p2s = 0)
dat_amelia <- imputationList(dat_amelia$imputations)

# Estimate models
mod <- list()
mod[['Listwise deletion']] <- lm(Clergy ~ Literacy + Commerce, dat)
mod[['Mice']] <- with(dat_mice, lm(Clergy ~ Literacy + Commerce))
mod[['Amelia']] <- MIcombine(with(dat_amelia, lm(Clergy ~ Literacy + Commerce)))

# Summarize
msummary(mod)
```
