---
title: "Getting started"
format: 
  html: default
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
    keep-tex: true
---

```{css, echo = FALSE}
.table, th, td {
  font-size: 0.9em;
} 
.table tbody td, .table thead tr {
    white-space: nowrap;
}
```

To begin, load the `modelsummary` package and download data from the
[Rdatasets archive](https://vincentarelbundock.github.io/Rdatasets/):

```{r, message = FALSE}
library(modelsummary)
library(tinytable)

url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url) 
dat$Small <- dat$Pop1831 > median(dat$Pop1831)
dat <- dat[, 
  c("Donations", "Literacy", "Commerce", "Crime_pers", "Crime_prop", "Clergy", "Small")
]
```

# Data Summaries

Quick overview of the data:

```{r}
datasummary_skim(dat)
```

Balance table (aka “Table 1”) with differences in means by subgroups:

```{r}
datasummary_balance(~Small, dat)
```

Correlation table:

```{r}
datasummary_correlation(dat)
```

Two variables and two statistics, nested in subgroups:

```{r}
datasummary(Literacy + Commerce ~ Small * (mean + sd), dat)
```

# Model Summaries

Estimate a linear model and display the results:

```{r}
mod <- lm(Donations ~ Crime_prop, data = dat)

modelsummary(mod)
```

Now estimate five regression models, display the results side-by-side, and use the `group_tt()` function from the `tinytable` package to add column labels:

```{r}
library(tinytable)

models <- list(
    "I" = lm(Donations ~ Literacy + Clergy, data = dat),
    "II" = lm(Crime_pers ~ Literacy + Clergy, data = dat),
    "III" = lm(Crime_prop ~ Literacy + Clergy, data = dat),
    "IV" = glm(Crime_pers ~ Literacy + Commerce, family = poisson, data = dat),
    "V" = glm(Donations ~ Literacy + Commerce, family = poisson, data = dat)
)

modelsummary(models, stars = TRUE, gof_omit = "IC|Adj|F|RMSE|Log") |>
    group_tt(j = list("Linear" = 1:3, "Poisson" = 4:5))
```

Now, save it to a Microsoft Word document:

```{r}
#| eval: false
modelsummary(models, output = "table.docx")
```

And draw a coefficient plot:


```{r}
# OLS models only
ols <- models[grepl("OLS", names(models))]
modelplot(ols, coef_omit = "Intercept")
```