```{r, include = FALSE}
options(modelsummary_factory_default = "tinytable")
```

```{css, include = FALSE}
.table, th, td {
  font-size: 0.9em;
} 
.table tbody td, .table thead td {
    white-space: nowrap;
}
```


# Getting started

To begin, load the `modelsummary` package and download data from the
[Rdatasets archive](https://vincentarelbundock.github.io/Rdatasets/):

```{r}
library(modelsummary)

url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url) 
dat$Small <- dat$Pop1831 > median(dat$Pop1831)
dat <- dat[, 
  c("Donations", "Literacy", "Commerce", "Crime_pers", "Crime_prop", "Clergy", "Small")
]
```

## Data Summaries

Quick overview of the data:

```{r}
datasummary_skim(dat)
```

Balance table (aka “Table 1”) with differences in means by subgroups:

```{r}
datasummary_balance(~Small, dat)
```

Correlation table:

```{r}
datasummary_correlation(dat)
```

Two variables and two statistics, nested in subgroups:

```{r}
datasummary(Literacy + Commerce ~ Small * (mean + sd), dat)
```

## Model Summaries

Estimate a linear model and display the results:

```{r}
mod <- lm(Donations ~ Crime_prop, data = dat)

modelsummary(mod)
```

Estimate five regression models, display the results side-by-side, and display the table:

```{r}
models <- list(
  "OLS 1"     = lm(Donations ~ Literacy + Clergy, data = dat),
  "Poisson 1" = glm(Donations ~ Literacy + Commerce, family = poisson, data = dat),
  "OLS 2"     = lm(Crime_pers ~ Literacy + Clergy, data = dat),
  "Poisson 2" = glm(Crime_pers ~ Literacy + Commerce, family = poisson, data = dat),
  "OLS 3"     = lm(Crime_prop ~ Literacy + Clergy, data = dat)
)

modelsummary(models, stars = TRUE, gof_omit = "IC|Adj|F|RMSE|Log")
```

Now, save it to a Microsoft Word document:

```{r}
#| eval: false
modelsummary(models, output = "table.docx")
```

And draw a coefficient plot:


```{r}
# OLS models only
ols <- models[grepl("OLS", names(models))]
modelplot(ols, coef_omit = "Intercept")
```