---
title: "modelsummary: regression tables with side-by-side models"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
tbody {
  font-size: .8em;
}
thead {
  font-size: .8em;
}
```

`modelsummary` includes a powerful set of utilities to customize the information displayed in your model summary tables. You can easily rename, reorder, subset or omit parameter estimates; choose the set of goodness-of-fit statistics to display; display various "robust" standard errors or confidence intervals; add titles, footnotes, or source notes; insert stars or custom characters to indicate levels of statistical significance; or add rows with supplemental information about your models.

```{r, message = FALSE}
library(modelsummary)
library(kableExtra)
library(gt)

url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url)

models <- list(
  "OLS 1"     = lm(Donations ~ Literacy + Clergy, data = dat),
  "Poisson 1" = glm(Donations ~ Literacy + Commerce, family = poisson, data = dat),
  "OLS 2"     = lm(Crime_pers ~ Literacy + Clergy, data = dat),
  "Poisson 2" = glm(Crime_pers ~ Literacy + Commerce, family = poisson, data = dat),
  "OLS 3"     = lm(Crime_prop ~ Literacy + Clergy, data = dat)
)

modelsummary(models)
```

# `modelsummary` function arguments

## output

The `output` argument determines the type of object returned by `modelsummary` and/or the file where this table should be written.

If you want to save a table directly to file, you can type:

```{r, eval=FALSE}
modelsummary(models, output = "table.docx")
modelsummary(models, output = "table.html")
modelsummary(models, output = "table.tex")
modelsummary(models, output = "table.md")
modelsummary(models, output = "table.txt")
modelsummary(models, output = "table.png")
```

If you want a raw HTML, LaTeX, or Markdown table, you can type:

```{r, eval=FALSE}
modelsummary(models, output = "html")
modelsummary(models, output = "latex")
modelsummary(models, output = "markdown")
```

If you to customize the appearance of your table using external tools like `gt`, `kableExtra`, `flextable`, or `huxtable`, you can type:

```{r, eval=FALSE}
modelsummary(models, output = "gt")
modelsummary(models, output = "kableExtra")
modelsummary(models, output = "flextable")
modelsummary(models, output = "huxtable")
```

Warning: When a file name is supplied to the `output` argument, the table is written immediately to file. If you want to customize your table by post-processing it with an external package, you need to choose a different output format and saving mechanism.  Unfortunately, the approach differs from package to package:

* `gt`: set `output="gt"`, post-process your table, and use the `gt::gtsave` function.
* `kableExtra`: set `output` to your destination format (e.g., "latex", "html", "markdown"), post-process your table, and use `kableExtra::save_kable` function.

## fmt

The `fmt` argument defines how numeric values are rounded and presented in the table. This argument accepts three types of input:

* Integer: Number of digits to keep after the period, including trailing zeros.
* String: Formatting string passed to the `sprintf` function. See `?sprintf` 
* Function: Returns a character string in the custom format you want.

For example:

```{r, eval=FALSE}
# 4 digits and trailing zero
modelsummary(models, fmt = 4)

# 4 digits and trailing zero: using sprintf()
modelsummary(models, fmt = "%.4f")

# scientific notation
modelsummary(models, fmt = "%.4e")
```

Custom formatting function with big mark commas:

```{r}
modf <- lm(I(mpg * 100) ~ hp, mtcars)
f <- function(x) formatC(x, digits = 2, big.mark = ",", format = "f")
modelsummary(modf, fmt = f, gof_map = NA)
```

In many languages the comma is used as a decimal mark instead of the period.  `modelsummary` respects the global `R` `OutDec` option, so you can simply execute this command and your tables will be adjusted automatically:

```{r, eval=FALSE}
options(OutDec=",")
```

## estimate

By default, `modelsummary` prints each coefficient estimate on its own row. You can customize this by changing the `estimate` argument. For example, this would produce a table of p values instead of coefficient estimates:

```{r, eval=FALSE}
modelsummary(models, estimate = "p.value")
```

You can also use [glue string](https://glue.tidyverse.org/), using curly braces to specify the statistics you want. For example, this displays the estimate next to a confidence interval: 

```{r}
modelsummary(
  models,
  fmt = 1,
  estimate  = "{estimate} [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_omit = "Intercept")
```

Glue strings can also apply R functions to estimates. However, since `modelsummary` rounds numbers and transforms them to character by default, we must set `fmt = NULL`:

```{r}
m <- glm(am ~ mpg, data = mtcars, family = binomial)
modelsummary(
    m,
    fmt = NULL,
    estimate = "{round(exp(estimate), 5)}",
    statistic = "{round(exp(estimate) * std.error, 3)}")
```

You can also use different estimates for different models by using a vector of strings:

```{r}
modelsummary(
  models,
  fmt = 1,
  estimate  = c("estimate",
                "{estimate}{stars}",
                "{estimate} ({std.error})",
                "{estimate} ({std.error}){stars}",
                "{estimate} [{conf.low}, {conf.high}]"),
  statistic = NULL,
  coef_omit = "Intercept")
```


## statistic

By default, `modelsummary` prints the coefficient's standard error in parentheses below the corresponding estimate. The value of this uncertainty statistic is determined by the `statistic` argument. The `statistic` argument accepts any of the column names produced by `get_estimates(model)`. For example:

```{r, eval=FALSE}
modelsummary(models, statistic = 'std.error')
modelsummary(models, statistic = 'p.value')
modelsummary(models, statistic = 'statistic')
```

You can also display confidence intervals in brackets by setting `statistic="conf.int"`:

```{r}
modelsummary(models,
             fmt = 1,
             statistic = 'conf.int', 
             conf_level = .99)
```

Alternatively, you can supply a [glue string](https://glue.tidyverse.org/) to get more complicated results:

```{r}
modelsummary(models,
             statistic = "{std.error} ({p.value})")
```

You can also display several different uncertainty estimates below the coefficient estimates by using a vector. For example,

```{r}
modelsummary(models, gof_omit = ".*",
             statistic = c("conf.int",
                           "s.e. = {std.error}", 
                           "t = {statistic}",
                           "p = {p.value}"))
```

Setting `statistic=NULL` omits all statistics. This can often be useful if, for example, you want to display confidence intervals next to coefficients: 

```{r}
modelsummary(models, gof_omit = ".*",
             estimate = "{estimate} [{conf.low}, {conf.high}]",
             statistic = NULL)
```

## vcov

You can use clustered or robust uncertainty estimates by modifying the `vcov` parameter. This function accepts 5 different types of input.  You can use a string or a vector of strings:

```r
modelsummary(models, vcov = "robust")
modelsummary(models, vcov = c("classical", "robust", "bootstrap", "stata", "HC4"))
```

These variance-covariance matrices are calculated using the `sandwich` package. You can pass arguments to the `sandwich` functions directly from the `modelsummary` function. For instance, to change the number of bootstrap replicates and to specify a clustering variable we could call:

```r
modelsummary(mod, vcov = "bootstrap", R = 1000, cluster = "country")
```

You can use a one-sided formula or list of one-sided formulas to use clustered standard errors:

```r
modelsummary(models, vcov = ~Region)
```

You can specify a function that produces variance-covariance matrices:

```r
library(sandwich)
modelsummary(models, vcov = vcovHC)
```

You can supply a list of functions of the same length as your model list:

```r
modelsummary(models, 
  vcov = list(vcov, vcovHC, vcovHAC, vcovHC, vcov))
```

You can supply a list of named variance-covariance matrices:

```r
vcov_matrices <- lapply(models, vcovHC)
modelsummary(models, vcov = vcov_matrices)
```

You can supply a list of named vectors:

```r
vc <- list(
  `OLS 1` = c(`(Intercept)` = 2, Literacy = 3, Clergy = 4), 
  `Poisson 1` = c(`(Intercept)` = 3, Literacy = -5, Commerce = 3),
  `OLS 2` = c(`(Intercept)` = 7, Literacy = -6, Clergy = 9), 
  `Poisson 2` = c(`(Intercept)` = 4, Literacy = -7, Commerce = -9),
  `OLS 3` = c(`(Intercept)` = 1, Literacy = -5, Clergy = -2))
modelsummary(models, vcov = vc)
```

## stars

Some people like to add "stars" to their model summary tables to mark statistical significance. The `stars` argument can take three types of input:

1. `NULL` omits any stars or special marks (default)
2. `TRUE` uses these default values: `+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001`
3. Named numeric vector for custom stars.

```r
modelsummary(models)
modelsummary(models, stars = TRUE) 
modelsummary(models, stars = c('+' = .1, '&' = .01)) 
```

Whenever `stars` is not `NULL`, `modelsummary` adds a note at the bottom of the table automatically. If you would like to add stars but *not* include a note at the bottom of the table, you can define the display of your estimate manually using a `glue` string, as described in the [`estimate` argument section of the documentation.](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#estimate-1) Whenever the `{stars}` string appears in the `estimate` or `statistic` arguments, `modelsummary` will assume that you want fine-grained control over your table, and will *not* include a note about stars.

```{r}
modelsummary(models,
             estimate = "{estimate}{stars}",
             gof_omit = ".*")
```

If you want to create your own stars description, you can add custom notes with the [`notes`](https://github.com/vincentarelbundock/modelsummary#notes) argument.

## coef: rename/omit/map

`modelsummary` offers powerful and innovative mechanisms to rename, reorder, and subset coefficients and goodness-of-fit statistics.

### coef_rename

You can rename coefficients using the `coef_rename` argument. For example, if you have two models with different explanatory variables, but you want both variables to have the same name and appear on the same row, you can do:

```{r}
x <- list(lm(hp ~ drat, mtcars),
          lm(hp ~ vs, mtcars))

modelsummary(x, coef_rename = c("drat" = "Explanator", "vs" = "Explanator"))
```

If you provide a named character vector to `coef_rename`, only exact matches of the *complete* original term name will be replaced.  

For complex modifications, you can feed a function which returns a named vector to the `coef_rename` argument. For example, `modelsummary` ships with a function called `coef_rename`, which executes some common renaming tasks automatically. This example also uses the `dvnames` function to extract the name of the dependent variable in each model:

```{r}
x <- list(
  lm(mpg ~ factor(cyl) + drat + disp, data = mtcars),
  lm(hp ~ factor(cyl) + drat + disp, data = mtcars)
)

modelsummary(dvnames(x), coef_rename = coef_rename)
```

Of course, you can also define your own custom functions. For instance, to rename a model with interacted variables (e.g., "drat:mpg"), you could define a custom `rename_explanator` function:

```{r}
y <- list(
  lm(hp ~ drat / mpg, mtcars),
  lm(hp ~ vs / mpg, mtcars)
)

rename_explanator <- function(old_names) {
  new_names <- gsub("drat|vs", "Explanator", old_names)
  setNames(new_names, old_names)
}

modelsummary(y, coef_rename = rename_explanator)
```

Beware of inadvertently replacing parts of other variable names! Making your regex pattern as specific as possible (e.g., by adding word boundaries) is likely a good idea. The custom rename function is also a good place to re-introduce the replacement of ":" with "×" if you are dealing with interaction terms -- `modelsummary` makes this replacement for you only when the `coef_rename` argument is not specified.

### coef_map

The `coef_map` argument is a named vector which allows users to rename, reorder, and subset coefficient estimates. Values of this vector correspond to the "clean" variable name. Names of this vector correspond to the "raw" variable name. The table will be sorted in the order in which terms are presented in `coef_map`. Coefficients which are *not* included in `coef_map` will be excluded from the table.

```{r}
cm <- c('Literacy'    = 'Literacy (%)',
        'Commerce'    = 'Patents per capita',
        '(Intercept)' = 'Constant')
modelsummary(models, coef_map = cm)
```

### coef_omit

An alternative mechanism to subset coefficients is to use the `coef_omit` argument. This string is a regular expression which will be fed to `stringr::str_detect` to detect the variable names which should be excluded from the table.

```{r}
modelsummary(models, coef_omit = "Intercept|.*merce", gof_map = NA)
```

Since `coef_omit` accepts regexes, you can do interesting things with it, such as specifying the list of variables that `modelsummary` should *keep* instead of omit. To do this, we use [a negative lookahead.](https://www.regular-expressions.info/lookaround.html) To keep only the coefficients *starting* with "Lit", we call:

```{r}
modelsummary(models, coef_omit = "^(?!Lit)", gof_map = NA)
```

To keep all coefficients matching the "y" substring:

```{r}
modelsummary(models, coef_omit = "^(?!.*y)", gof_map = NA)
```

To keep all coefficients matching one of two substrings:

```{r}
modelsummary(models, coef_omit = "^(?!.*tercept|.*y)", gof_map = NA)
```

## gof_omit

`gof_omit` is a regular expression which will be fed to `stringr::str_detect` to detect the names of the statistics which should be excluded from the table.

```r
modelsummary(models, gof_omit = 'DF|Deviance|R2|AIC|BIC')
```

## gof_map

The `gof_map` argument can be used to rename, re-order, subset, and format the statistics displayed in the bottom section of the table ("goodness-of-fit").

The first type of values allowed is a character vector with elements equal to column names in the data.frame produced by `get_gof(model)`:

```{r}
modelsummary(models, gof_map = c("nobs", "r.squared"))
```

A more powerful mechanism is to supply a `data.frame` (or `tibble`) through the `gof_map` argument. This data.frame must include 3 columns:

1. `raw`: a string with the name of a column produced by `broom::glance(model)`.
2. `clean`: a string with the "clean" name of the statistic you want to appear in your final table.
3. `fmt`: a string which will be used to round/format the string in question (e.g., `"%.3f"`). This follows the same standards as the `fmt` argument in `?modelsummary`.

You can see an example of a valid data frame by typing `modelsummary::gof_map`. This is the default data.frame that `modelsummary` uses to subset and reorder goodness-of-fit statistics. As you can see, `omit == TRUE` for quite a number of statistics. You can include setting `omit == FALSE`: 

```r
gm <- modelsummary::gof_map
gm$omit <- FALSE
modelsummary(models, gof_map = gm)
```

The goodness-of-fit statistics will be printed in the table in the same order as in the `gof_map` data.frame.

```r
f <- function(x) format(round(x, 3), big.mark=",")
gm <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = f),
  list("raw" = "AIC", "clean" = "aic", "fmt" = f))
modelsummary(models, gof_map = gm)
```

Notice the subtle difference between `coef_map` and `gof_map`. On the one hand, `coef_map` works as a "white list": any coefficient not explicitly entered will be omitted from the table. On the other, `gof_map` works as a "black list": statistics need to be explicitly marked for omission.

Another convenient way to build a `gof_map` argument is to use the `tribble` function from the `tibble` package. In this example, we insert special HTML code to display a superscript, so we use the `escape=FALSE` argument:

```{r}
gm <- tibble::tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "N",             0,
  "r.squared", "R<sup>2</sup>", 2)

modelsummary(
  models,
  statistic = NULL,
  gof_map = gm,
  escape = FALSE)
```

## shape

The `shape` argument accepts a formula which determines the structure of the table, and can display "grouped" coefficients together (e.g., multivariate outcome or mixed-effects models). The left side of the formula represents the rows and the right side represents the columns. 

The default formula is `term + statistic ~ model`:

```{r}
m <- list(
    lm(mpg ~ hp, data = mtcars),
    lm(mpg ~ hp + drat, data = mtcars))

modelsummary(m, shape = term + statistic ~ model, gof_map = NA)
```

We can display statistics horizontally with:

```{r}
modelsummary(m,
             shape = term ~ model + statistic,
             statistic = "conf.int",
             gof_map = NA)
```

The order of terms in the formula determines the order of headers in the table.


```{r}
modelsummary(m,
             shape = term ~ statistic + model,
             statistic = "conf.int",
             gof_map = NA)
```

`shape` does partial matching and will try to fill-in incomplete formulas:

```{r, eval = FALSE}
modelsummary(m, shape = ~ statistic)
```

Some models like multinomial logit or GAMLSS produce "grouped" parameter estimates. To display these groups, we can include a group identifier in the `shape` formula. This group identifier must be one of the column names produced by `get_estimates(model)`. For example, in models produced by `nnet::multinom`, the group identifier is called "response":

```{r, message = FALSE}
library(nnet)

dat_multinom <- mtcars
dat_multinom$cyl <- sprintf("Cyl: %s", dat_multinom$cyl)

mod <- list(
    nnet::multinom(cyl ~ mpg, data = dat_multinom, trace = FALSE),
    nnet::multinom(cyl ~ mpg + drat, data = dat_multinom, trace = FALSE))

get_estimates(mod[[1]])
```

To summarize the results, we can type: 

```{r, warning=FALSE}
modelsummary(mod, shape = term + response ~ statistic)
```

The terms of the `shape` formula above can of course be rearranged to reshape the table. For example:

```{r, warning=FALSE}
modelsummary(mod, shape = model + term ~ response)
```

## align

By default, `modelsummary` will align the first column (with coefficient names) to the left, and will center the results columns. To change this default, you can use the align argument, which accepts a string of the same length as the number of columns:

```{r, eval=FALSE}
modelsummary(models, align="lrrrrr")
```

Users who produce PDF documents using Rmarkdown or LaTeX can also align values on the decimal dot by using the character "d" in the `align` argument:

```{r, eval=FALSE}
modelsummary(models, align="lddddd")
```

For the table produced by this code to compile, users must include the following code in their LaTeX preamble:

```{latex, eval=FALSE}
\usepackage{booktabs}
\usepackage{siunitx}
\newcolumntype{d}{S[input-symbols = ()]}
```

## notes

Add notes to the bottom of your table:

```r
modelsummary(models, 
   notes = list('Text of the first note.', 
                'Text of the second note.'))
```

## title

You can add a title to your table as follows:

```r
modelsummary(models, title = 'This is a title for my table.')
```

## `add_rows`

Use the `add_rows` argument to add rows manually to a table. For example, let's say you estimate two models with a factor variables and you want to insert (a) an empty line to identify the category of reference, and (b) customized information at the bottom of the table:

```{r}
models <- list()
models[['OLS']] <- lm(mpg ~ factor(cyl), mtcars)
models[['Logit']] <- glm(am ~ factor(cyl), mtcars, family = binomial)
```

We create a data.frame with the same number of columns as the summary table. Then, we define a "position" attribute to specify where the new rows should be inserted in the table. Finally, we pass this data.frame to the `add_rows` argument:

```{r}
library(tibble)
rows <- tribble(~term,          ~OLS,  ~Logit,
                'factor(cyl)4', '-',   '-',
                'Info',         '???', 'XYZ')
attr(rows, 'position') <- c(3, 9)

modelsummary(models, add_rows = rows)
```

## `exponentiate`

We can exponentiate their estimates using the `exponentiate` argument:

```{r}
mod_logit <- glm(am ~ mpg, data = mtcars, family = binomial)
modelsummary(mod_logit, exponentiate = TRUE)
```

We can also present exponentiated and standard models side by side by using a logical vector:

```{r}
mod_logit <- list(mod_logit, mod_logit)
modelsummary(mod_logit, exponentiate = c(TRUE, FALSE))
```

# `...` ellipsis: Additional arguments

All arguments passed by the user to a `modelsummary` function are pushed forward in two other functions:

1. The function which extracts model estimates.
   - By default, additional arguments are pushed forward to `broom::tidy` and `broom::glance`. Users can also can also use a different "backend" to extract information from model objects: the `parameters` and `performance` packages. By setting the `modelsummary_get` global option, we tell `modelsummary` to use the `easystats`/`parameters` packages instead of `broom`. With these packages, other arguments are available, such as the `metrics` argument. Please refer to these package's documentation to details.
2. The table-making functions.
   - By default, additional arguments are pushed forward to `kableExtra::kbl`, but users can use a different table-making function by setting the `output` argument to a different value such as `"gt"`, `"flextable"`, or `"huxtable"`.
   - See [the Appearance vignette](https://vincentarelbundock.github.io/modelsummary/articles/appearance.html) for examples.

All arguments passed supported by these functions are thus automatically available directly in `modelsummary`, `modelplot`, and the `datasummary` family of functions.

# Custom appearance

To customize the appearance of tables, `modelsummary` supports four popular and extremely powerful table-making packages: 

1. [`gt`: https://gt.rstudio.com](https://gt.rstudio.com)
2. [`kableExtra`: http://haozhu233.github.io/kableExtra](http://haozhu233.github.io/kableExtra)
3. [`huxtable`: https://hughjonesd.github.io/huxtable/](https://hughjonesd.github.io/huxtable/)
4. [`flextable`: https://davidgohel.github.io/flextable/](https://davidgohel.github.io/flextable/)

The ["customizing the look of your tables" vignette](https://vincentarelbundock.github.io/modelsummary/articles/appearance.html) shows examples for all 4 packages.

# Supported models

`modelsummary` automatically supports all the models supported by the `tidy` function of the [broom package](broom.tidymodels.org) or the `parameters` function of the [parameters package](https://easystats.github.io/parameters/). The list of supported models is rapidly expanding. At the moment, it covers the following model classes:

```{r}
supported_models()
```

To see if a given model is supported, you can fit it, and then call this function:

```{r, eval=FALSE}
get_estimates(model)
```

If this function does not return a valid output, you can easily (really!!) add your own support. See the next section for a tutorial. If you do this, you may consider opening an issue on the Github website of the `broom` package: https://github.com/tidymodels/broom/issues

# Adding new models (part I)

The simplest way to summarize an unsupported model is to create a `modelsummary_list` object. This approach is super flexible, but it requires manual intervention, and it can become tedious if you need to summarize many models. The next section shows how to add formal support for an unsupported model type.

A `modelsummary_list` is a list with two element that conform to the `broom` package specification: `tidy` and `glance`. `tidy` is a data.frame with at least three columns: `term`, `estimate`, and `std.error`. `glance` is a data.frame with only a single row, and where each column will be displayed at the bottom of the table in the goodness-of-fit section. Finally, we wrap those two elements in a list and assign it a `modelsummary_list` class:

```{r}
ti <- data.frame(
  term = c("coef1", "coef2", "coef3"),
  estimate = 1:3,
  std.error = c(pi, exp(1), sqrt(2)))

gl <- data.frame(
  stat1 = "blah",
  stat2 = "blah blah")

mod <- list(
  tidy = ti,
  glance = gl)
class(mod) <- "modelsummary_list"

modelsummary(mod)
```

# Adding new models (part II)

`modelsummary` relies on two functions from the `broom` package to extract model information: `tidy` and `glance`. If `broom` doesn't support the type of model you are trying to summarize, `modelsummary` won't support it out of the box. Thankfully, it is extremely easy to add support for most models using custom methods.

For example, models produced by the `MCMCglmm` package are not currently supported by `broom`. To add support, you simply need to create a `tidy` and a `glance` method:

```r
# load packages and data
library(modelsummary)
library(MCMCglmm)
data(PlodiaPO)

# add custom functions to extract estimates (tidy) and goodness-of-fit (glance) information
tidy.MCMCglmm <- function(x, ...) {
    s <- summary(x, ...)
    ret <- data.frame(
      term      = row.names(s$solutions),
      estimate  = s$solutions[, 1],
      conf.low  = s$solutions[, 2],
      conf.high = s$solutions[, 3])
    ret
}

glance.MCMCglmm <- function(x, ...) {
    ret <- data.frame(
      dic = x$DIC,
      n   = nrow(x$X))
    ret
}

# estimate a simple model
model <- MCMCglmm(PO ~ 1 + plate, random = ~ FSfamily, data = PlodiaPO, verbose=FALSE, pr=TRUE)

# summarize the model
modelsummary(model, statistic = 'conf.int')
```

Two important things to note. First, the methods are named `tidy.MCMCglmm` and `glance.MCMCglmm` because the model object I am trying to summarize is of class `MCMCglmm`. You can find the class of a model by running: `class(model)`.

Second, in the example above, we used the `statistic = 'conf.int'` argument. This is because the `tidy` method produces `conf.low` and `conf.high` columns. In most cases, users will define `std.error` column in their custom `tidy` methods, so the `statistic` argument will need to be adjusted.

If you create new `tidy` and `glance` methods, please consider contributing them to `broom` so that the rest of the community can benefit from your work: https://github.com/tidymodels/broom

# Adding new information to existing models

Users may want to include more information than is made available by the default extractor function. For example, models produced by the `MASS::polr` do not produce p values by default, which means that we cannot use the `stars=TRUE` argument in `modelsummary`. However, it is possible to extract this information by using the `lmtest::coeftest` function. To include such custom information, we will define new `glance_custom` and `tidy_custom` methods. 

We begin by estimating a model with the `MASS::polr`:

```{r}
library(MASS)

mod_ordinal <- polr(as.ordered(gear) ~ mpg + drat, data = mtcars)

get_estimates(mod_ordinal)
```

The `get_estimates` function shows that our default extractor does *not* produce a `p.value` column. As a result, setting `stars=TRUE` in `modelsummary` will produce an error.

We know that the `MASS::polr` produces an object of class `polr`:

```{r}
class(mod_ordinal)
```

To extract more (custom) information from a model of this class, we thus define a method called `tidy_custom.polr` which returns a data.frame with two columns: `term` and `p.value`:

```{r}
tidy_custom.polr <- function(x, ...) {
  s <- lmtest::coeftest(x)
  out <- data.frame(
    term = row.names(s),
    p.value = s[, "Pr(>|t|)"])
  out
}
```

When this method is defined, `modelsummary` can automatically extract p values from all models of this class, and will now work properly with `stars=TRUE`:

```{r, warning=FALSE, message=FALSE}
modelsummary(mod_ordinal, stars = TRUE)
```

# Customizing existing models (part I)

Sometimes users will want to include information that is not supplied by those functions. A pretty easy way to include extra information is to define new `glance_custom` and `tidy_custom` methods. To illustrate, we estimate two linear regression models using the `lm` function:

```{r}
library(modelsummary)

mod <- list()
mod[[1]] <- lm(hp ~ mpg + drat, mtcars)
mod[[2]] <- lm(wt ~ mpg + drat + am, mtcars)
```

In `R`, the `lm` function produces models of class "lm":

```{r}
class(mod[[1]])
```

Let's say you would like to print the dependent variable for each model of this particular class. All you need to do is define a new method called `glance_custom.lm`. This method should return a data.frame (or tibble) with 1 row, and 1 column per piece of information you want to display. For example:

```{r}
glance_custom.lm <- function(x, ...) {
    dv <- as.character(formula(x)[2])
    out <- data.frame("DV" = dv)
    return(out)
}
```

Now, let's customize the body of the table. The `vcov` argument already allows users to customize uncertainty estimates. But imagine you want to override the *coefficient estimates* of your "lm" models. Easy! All you need to do is define a `tidy_custom.lm` method which returns a data.frame (or tibble) with one column called "term" and one column called "estimate".

Here, we'll substitute estimates by an up/down-pointing triangles which represents their signs:

```{r}
tidy_custom.lm <- function(x, ...) {
    s <- summary(x)$coefficients
    out <- data.frame(
      term = row.names(s),
      estimate = ifelse(s[,1] > 0, '▲', '▼'))
    return(out)
}
```

After you define the `glance_custom` and `tidy_custom` methods, `modelsummary` will automatically display your customized model information:

```{r}
modelsummary(mod)
```

Note that you can define a `std.error` column in `tidy_custom.lm` to replace the uncertainty estimates instead of the coefficients.

```{r, include=FALSE}
rm("tidy_custom.lm")
rm("glance_custom.lm")
```

# Customizing existing models (part II)

An even more fundamental way to customize the output would be to completely bypass `modelsummary`'s extractor functions by assigning a new class name to your model. For example, 

```{r}
# estimate a linear model
mod_custom <- lm(hp ~ mpg + drat, mtcars)

# assign it a new class
class(mod_custom) <- c("custom", class(mod_custom))

# define tidy and glance methods
tidy.custom <- function(x, ...) {
  data.frame(
    term = names(coef(x)),
    estimate = letters[1:length(coef(x))],
    std.error = seq_along(coef(x))
  )
}

glance.custom <- function(x, ...) {
  data.frame(
    "Model" = "Custom",
    "nobs" = stats::nobs(x)
  )
}

# summarize
modelsummary(mod_custom)
```

Warning: When defining new `tidy` and `glance` methods, it is important to include an ellipsis argument (`...`).

# Customizing existing models (part III)

Another flexible way to customize model output is to use `output = "modelsummary_list"`.
With this output option, `modelsummary()` returns a list with two elements:
`tidy` contains parameter estimates, standard errors, etc., and `glance` contains
model statistics such as the AIC. For example,

```{r}
mod <- lm(hp ~ mpg + drat, mtcars)
mod_list <- modelsummary(mod, output = "modelsummary_list")
mod_list$tidy
mod_list$glance
```
Both `tidy` and `glance` can now be customized, and the updated model can be passed
back to modelsummary using `modelsummary(mod_list)`.
All information that is displayed in the table is contained in `mod_list`, so
this pattern allows for very flexible adjustments of output tables.

A useful example for this pattern concerns mixed models using `lme4`. Assume we want to 
compare the effect of using different degrees-of-freedom adjustments on the significance 
of the coefficients. The models have identical parameter estimates, standard errors, and
model fit statistics - we only want to change the p-values.
We use the `parameters` package to compute the adjusted p-values.

```{r include = FALSE}
library("lme4")
```

```{r}
library("lme4")
mod <- lmer(mpg ~ drat + (1 | am), data = mtcars)
mod_list <- modelsummary(mod, output = "modelsummary_list", effects = "fixed")
# create a copy, where we'll change the p-values
mod_list_kenward <- as.list(mod_list)
mod_list_kenward$tidy$p.value <- parameters::p_value_kenward(mod)$p

modelsummary(list("Wald" = mod_list, "Kenward" = mod_list_kenward), 
            statistic = "{std.error} ({p.value}) {stars}")
```

# Rmarkdown

You can use `modelsummary` to insert tables into dynamic documents with `knitr` or `Rmarkdown`. This minimal .Rmd file can produce tables in PDF, HTML, or RTF documents:

* [minimal.Rmd](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/minimal.Rmd)

This .Rmd file shows illustrates how to use table numbering and cross-references to produce PDF documents using `bookdown`:

* [cross_references.Rmd](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/cross_references.Rmd)

This .Rmd file shows how to customize tables in PDF and HTML files using `gt` and `kableExtra` functions:

* [appearance.Rmd](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/appearance.Rmd)

# Quarto

[Quarto is an open source publishing system](https://quarto.org/) built on top of Pandoc. It was designed as a "successor" to Rmarkdown, and includes useful features for technical writing, such as built-in support for cross-references. `modelsummary` works automatically with Quarto. This is a minimal document with cross-references which should render automatically to PDF, HTML, and more:

````{r, eval = FALSE}
---
format: pdf
title: Example
---

@tbl-mtcars shows that cars with high horse power get low miles per gallon.

```{r}
#| label: tbl-mtcars
#| tbl-cap: "Horse Powers vs. Miles per Gallon"
library(modelsummary)
mod <- lm(mpg ~ hp, mtcars)
modelsummary(mod)
```
````


# Emacs Org-Mode

You can use `modelsummary` to insert tables into Emacs Org-Mode documents, which can be exported to a variety of formats, including HTML and PDF (via LaTeX). As with anything Emacs-related, there are many ways to achieve the outcomes you want. Here is one example of an Org-Mode document which can automatically export tables to HTML and PDF without manual tweaks:

````
#+PROPERTY: header-args:R :var orgbackend=(prin1-to-string org-export-current-backend)
#+MACRO: Rtable (eval (concat "#+header: :results output " (prin1-to-string org-export-current-backend)))

{{{Rtable}}}
#+BEGIN_SRC R :exports both
library(modelsummary)
options(modelsummary_factory_default = orgbackend)

mod = lm(hp ~ mpg, data = mtcars)

modelsummary(mod)
#+END_SRC
````

The first line tells Org-mode to assign a variable called `orgbackend`. This variable will be accessible by the `R` session, and will be equal to "html" or "latex", depending on the export format.

The second line creates an Org macro which we will use to automatically add useful information to the header of source blocks. For instance, when we export to HTML, the macro will expand to `:results output html`. This tells Org-Mode to insert the last printed output from the `R` session, and to treat it as raw HTML. 

The `{{{Rtable}}}` call expands the macro to add information to the header of the block that follows.

`#+BEGIN_SRC R :exports both` says that we want to print both the original code and the output (`:exports results` would omit the code, for example).

Finally, `options(modelsummary_factory_default=orgbackend` uses the variable we defined to set the default output format. That way, we don't have to use the `output` argument every time.

One potentially issue to keep in mind is that the code above extracts the printout from the `R` console. However, when we customize tables with `kableExtra` or `gt` functions, those functions do not always return printed raw HTML or LaTeX code. Sometimes, it can be necessary to add a call to `cat` at the end of a table customization pipeline. For example:

````
{{{Rtable}}}
#+BEGIN_SRC R :exports both
library(modelsummary)
library(kableExtra)

mod = lm(hp ~ mpg, data = mtcars)

modelsummary(mod, output = orgbackend) %>%
  row_spec(1, background = "pink") %>%
  cat()
#+END_SRC
````

# Global options

Users can change the default behavior of `modelsummary` by setting global options.

Omit the note at the bottom of the table with significance threshold:

```{r, eval = FALSE}
options("modelsummary_stars_note" = FALSE)
```

Change the default output format:

```{r, eval = FALSE}
options(modelsummary_factory_default = "latex")
options(modelsummary_factory_default = "gt")
```

Change the backend packages that `modelsummary` uses to create tables in different output formats:

```{r, eval = FALSE}
options(modelsummary_factory_html = 'kableExtra')
options(modelsummary_factory_latex = 'flextable')
options(modelsummary_factory_word = 'huxtable')
options(modelsummary_factory_png = 'gt')
```

Change the packages that `modelsummary` uses to extract information from models:

```{r, eval = FALSE}
# tidymodels: broom 
options(modelsummary_get = "broom")

# easystats: performance + parameters
options(modelsummary_get = "easystats")
```

[The `appearance` vignette](https://vincentarelbundock.github.io/modelsummary/articles/appearance.html#themes) shows how to set "themes" for your tables using the `modelsummary_theme_gt`, `modelsummary_theme_kableExtra`, `modelsummary_theme_flextable` and `modelsummary_theme_huxtable` global options. For example:

```{r, eval=FALSE}
library(gt)

# The ... ellipsis is required!
custom_theme <- function(x, ...) {
    x %>% gt::opt_row_striping(row_striping = TRUE)
}
options("modelsummary_theme_gt" = custom_theme)

mod <- lm(mpg ~ hp + drat, mtcars)
modelsummary(mod, output = "gt")
```

# Case studies

## Subgroup estimation with `nest_by`

Sometimes, it is useful to estimate multiple regression models on subsets of the data. To do this efficiently, we can use the `nest_by` function from the `dplyr` package. Then, estimate the models with `lm`, extract them and name them with `pull`, and finally summarize them with `modelsummary`:

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

mtcars %>%
    nest_by(cyl) %>%
    mutate(models = list(lm(mpg ~ hp, data))) %>%
    pull(models, name = cyl) %>%
    modelsummary
```

## Statistics in separate columns instead of one over the other

In somes cases, you may want to display statistics in separate columns instead of one over the other. It is easy to achieve this outcome by using the `estimate` argument. This argument accepts a vector of values, one for each of the models we are trying to summarize. If we want to include estimates and standard errors in separate columns, all we need to do is repeat a model, but request different statistics. For example,

```{r}
library(modelsummary)
library(kableExtra)

mod1 <- lm(mpg ~ hp, mtcars)
mod2 <- lm(mpg ~ hp + drat, mtcars)

models <- list(
    "Coef."     = mod1,
    "Std.Error" = mod1,
    "Coef."     = mod2,
    "Std.Error" = mod2)

modelsummary(models,
             estimate = c("estimate", "std.error", "estimate", "std.error"),
             statistic = NULL,
             gof_omit = ".*") %>%
    add_header_above(c(" " = 1, "Model A" = 2, "Model B" = 2))
```

This can be automated using a simple function:

```{r}
side_by_side <- function(models, estimates, ...) {
    models <- rep(models, each = length(estimates))
    estimates <- rep(estimates, times = 2)
    names(models) <- names(estimates)
    modelsummary(models = models, estimate = estimates,
                 statistic = NULL, gof_omit = ".*", ...)
}

models = list(
    lm(mpg ~ hp, mtcars),
    lm(mpg ~ hp + drat, mtcars))

estimates <- c("Coef." = "estimate", "Std.Error" = "std.error")

side_by_side(models, estimates = estimates)
```

## Bootstrap

Users often want to use estimates or standard errors that have been obtained using a custom strategy. To achieve this in an automated and replicable way, it can be useful to use the `tidy_custom` strategy described above in the "Cutomizing Existing Models" section. 

For example, we can use the `modelr` package to draw 500 resamples of a dataset, and compute bootstrap standard errors by taking the standard deviation of estimates computed in all of those resampled datasets. To do this, we defined `tidy_custom.lm` function that will automatically bootstrap any `lm` model supplied to `modelsummary`, and replace the values in the table automatically.

Note that the `tidy_custom_lm` returns a data.frame with 3 columns: `term`, `estimate`, and `std.error`: 

```{r, message=FALSE}
library("modelsummary")
library("broom")
library("tidyverse")
library("modelr")

tidy_custom.lm <- function(x, ...) {
  # extract data from the model
  model.frame(x) %>%
    # draw 500 bootstrap resamples
    modelr::bootstrap(n = 500) %>%
    # estimate the model 500 times
    mutate(results = map(strap, ~ update(x, data = .))) %>%
    # extract results using `broom::tidy`
    mutate(results = map(results, tidy)) %>%
    # unnest and summarize
    unnest(results) %>%
    group_by(term) %>%
    summarize(std.error = sd(estimate),
              estimate = mean(estimate))
}

mod = list(
  lm(hp ~ mpg, mtcars) ,
  lm(hp ~ mpg + drat, mtcars))

modelsummary(mod)
```

```{r, include=FALSE}
rm("tidy_custom.lm")
```

## `fixest`: Fixed effects and instrumental variable regression

One common use-case for `glance_custom` is to include additional goodness-of-fit statistics. For example, in an instrumental variable estimation computed by the `fixest` package, we may want to include an IV-Wald statistic for the first-stage regression of each endogenous regressor:

```{r, message=FALSE}
library(fixest)
library(tidyverse)

# create a toy dataset
base <- iris
names(base) <- c("y", "x1", "x_endo_1", "x_inst_1", "fe")
base$x_inst_2 <- 0.2 * base$y + 0.2 * base$x_endo_1 + rnorm(150, sd = 0.5)
base$x_endo_2 <- 0.2 * base$y - 0.2 * base$x_inst_1 + rnorm(150, sd = 0.5)

# estimate an instrumental variable model
mod <- feols(y ~ x1 | fe | x_endo_1 + x_endo_2 ~ x_inst_1 + x_inst_2, base)

# custom extractor function returns a one-row data.frame (or tibble)
glance_custom.fixest <- function(x) {
  tibble(
    "Wald (x_endo_1)" = fitstat(x, "ivwald")[[1]]$stat,
    "Wald (x_endo_2)" = fitstat(x, "ivwald")[[2]]$stat
  )
}

# draw table
modelsummary(mod)
```

```{r, include=FALSE}
rm("glance_custom.fixest")
```

## Multiple imputation

`modelsummary` can pool and display analyses on several datasets imputed using the `mice` or `Amelia` packages. This code illustrates how:

```{r, message=FALSE}
library(mice)
library(Amelia)
library(modelsummary)

# Download data from `Rdatasets`
url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url)[, c('Clergy', 'Commerce', 'Literacy')]

# Insert missing values
dat$Clergy[sample(1:nrow(dat), 10)] <- NA
dat$Commerce[sample(1:nrow(dat), 10)] <- NA
dat$Literacy[sample(1:nrow(dat), 10)] <- NA

# Impute with `mice` and `Amelia`
dat_mice <- mice(dat, m = 5, printFlag = FALSE)
dat_amelia <- amelia(dat, m = 5, p2s = 0)$imputations

# Estimate models
mod <- list()
mod[['Listwise deletion']] <- lm(Clergy ~ Literacy + Commerce, dat)
mod[['Mice']] <- with(dat_mice, lm(Clergy ~ Literacy + Commerce)) 
mod[['Amelia']] <- lapply(dat_amelia, function(x) lm(Clergy ~ Literacy + Commerce, x))

# Pool results
mod[['Mice']] <- mice::pool(mod[['Mice']])
mod[['Amelia']] <- mice::pool(mod[['Amelia']])

# Summarize
modelsummary(mod)
```

# Backends

The table-making backends supported by `modelsummary` have overlapping capabilities (e.g., several of them can produce HTML tables). These are the default packages used for different outputs:

`kableExtra`:

* HTML
* LaTeX / PDF

`flextable`:

* Word
* Powerpoint

`gt`:

* jpg
* png

You can modify these defaults by setting global options such as:

```r
options(modelsummary_factory_html = "kableExtra")
options(modelsummary_factory_latex = "gt")
options(modelsummary_factory_word = "huxtable")
options(modelsummary_factory_png = "gt")
```

# FAQ

## Stack Overflow is useful

* [Standardized coefficients](https://stackoverflow.com/questions/72266343/how-do-i-get-standardized-beta-coefficients-using-modelsummary-in-r-and-how-to/72267006#72267006)

## Where can I get help?

First, please read the documentation in `?modelsummary` and on [the `modelsummary` website.](https://vincentarelbundock.github.io/modelsummary/) The website includes dozens of worked examples and a lot of detailed explanation.

Second, try to [use the `[modelsummary]` tag on StackOverflow.](https://stackoverflow.com/search?tab=newest&q=%5br%5d%20modelsummary)

Third, if you think you found a bug or have a feature request, please file it on the Github issue tracker: 

## How can I add or modify statistics in a table?

See the detailed documentation in the ["Adding and Customizing Models" section of the `modelsummary` website.](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html)

## How does `modelsummary` extract estimates and goodness-of-fit statistics?

A `modelsummary` table is divided in two parts: "Estimates" (top of the table) and "Goodness-of-fit" (bottom of the table). To populate those two parts, `modelsummary` tries using the `broom`, `parameters` and `performance` packages in sequence.

Estimates:

1. Try the `broom::tidy` function to see if that package supports this model type, or if the user defined a custom `tidy` function in their global environment. If this fails...
2. Try the `parameters::model_parameters` function to see if the `parameters` package supports this model type.

Goodness-of-fit:

1. Try the `broom::glance` function to see if that package supports this model type, or if the user defined a custom `glance` function in their global environment. If this fails...
2. Try the `performance::model_performance` function to see if the `performance` package supports this model type.

You can change the order in which those steps are executed by setting a global option:

```{r, eval=FALSE}
# tidymodels: broom 
options(modelsummary_get = "broom")

# easystats: performance + parameters
options(modelsummary_get = "easystats")
```

If all of this fails, `modelsummary` will return an error message.


If you have problems with a model object, you can often diagnose the problem by running the following commands from a *clean* R session:

```r
# see if broom supports your model type
library(broom)
tidy(model)
glance(model)

# see if parameters and performance support your model type
library(parameters)
library(performance)
model_parameters(model)
model_performance(model)

# see if broom.mixed supports your model type
library(broom.mixed)
tidy(model)
glance(model)
```

If none of these options work, you can create your own `tidy` and `glance` methods, as described in the [Adding new models section.](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#adding-new-models-1)

If one of the extractor functions does not work well or takes too long to process, you can define a new "custom" model class and choose your own extractors, as described in the [Adding new models section.](https://vincentarelbundock.github.io/modelsummary/articles/modelsummary.html#adding-new-models-1)

## How can I speed up `modelsummary`?

The `modelsummary` function, by itself, is *not* slow: it should only take a couple seconds to produce a table in any output format. However, sometimes it can be computationally expensive (and long) to extract estimates and to compute goodness-of-fit statistics for your model.

The main options to speed up `modelsummary` are:

1. Set `gof_map=NA` to avoid computing expensive goodness-of-fit statistics.
2. Use the `easystats` extractor functions and the `metrics` argument to avoid computing expensive statistics (see below for an example).
3. Use parallel computation if you are summarizing multiple models. See the "Parallel computation" section in the `?modelsummary` documentation.

To diagnose the slowdown and find the bottleneck, you can try to benchmark the various extractor functions:

```{r}
library(tictoc)

data(trade)
mod <- lm(mpg ~ hp + drat, mtcars)

tic("tidy")
x <- broom::tidy(mod)
toc()

tic("glance")
x <- broom::glance(mod)
toc()

tic("parameters")
x <- parameters::parameters(mod)
toc()

tic("performance")
x <- performance::performance(mod)
toc()
```

In my experience, the main bottleneck tends to be computing goodness-of-fit statistics. The `performance` extractor allows users to specify a `metrics` argument to select a subset of GOF to include. Using this can speedup things considerably.

First, we set a global option to run the `performance` extractor first, before `broom::glance`:

```{r}
options(modelsummary_get = "easystats")
```

Then, we call `modelsummary` with the `metrics` argument:

```{r}
modelsummary(mod, metrics = "rmse")
```

Going back to the original setting:

```{r}
options(modelsummary_get = "broom")
```

## Escaped LaTeX characters

Sometimes, users want to include raw LaTeX commands in their tables, such as coefficient names including math mode: `Apple $\times$ Orange`. The result of these attempts is often a weird string such as: `\$\textbackslash{}times\$` instead of proper LaTeX-rendered characters.

The source of the problem is that `kableExtra`, default table-making package in `modelsummary`, automatically escapes weird characters to make sure that your tables compile properly in LaTeX. To avoid this, we need to pass the `escape=FALSE` to `modelsummary`:

```{r, eval=FALSE}
modelsummary(mod, escape = FALSE)
```
