---
title: '`modelplot`: Plot model coefficients with confidence intervals'
output:
  html_document: default
  pdf_document:
      latex_engine: xelatex
---

<link rel="stylesheet" href="https://fonts.googleapis.com/css?family=Roboto">
<style>
tbody {
  font-family: 'DejaVu Sans', 'Roboto', 'Georgia', 'Times', 'Roboto', 'DejaVu Serif', serif;
}
</style>


```{r, echo=FALSE, message=FALSE}
library(modelsummary)
library(tidyverse)
options(modelsummary_default = 'kableExtra')
```

`modelplot` is a function from the `modelsummary` package. It allows you to plot model estimates and confidence intervals. It makes it easy to subset, rename, reorder, and customize plots using same mechanics as in `modelsummary`.

To illustrate how the function works, we fit a linear model to data about the [Palmer Penguins](https://github.com/allisonhorst/palmerpenguins):

```{r}
url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/palmerpenguins/penguins.csv'
dat <- read.csv(url)

# rescale mm -> cm
dat$culmen_length_cm <- dat$culmen_length_mm / 10
dat$flipper_length_cm <- dat$flipper_length_mm / 10

mod <- lm(culmen_length_cm ~ flipper_length_cm + species, data = dat)
```

Then, we load the `modelsummary` library and call `modelplot`:

```{r, fig.height=2}
library(modelsummary)

modelplot(mod)
```

# Rename, reorder, subset

`modelplot` uses the same mechanics as `modelsummary` to rename, reorder, and subset estimates. First, you can use the `coef_omit` argument. This will omit any coefficient that matches a string or regular expression. To omit the intercept, for example, we can type:

```{r, fig.height=2}
modelplot(mod, coef_omit = 'Interc')
```

Second, you can use the `coef_map` argument. `coef_map` is a named character vector, where names correpond to the original term names, and values correspond the names you want to assign. Any variable that is *not* included in `coef_map` will be excluded. Variables will also be drawn in the same order as in `coef_map`:

```{r, fig.height=2}
cm <- c('speciesChinstrap' = 'Chinstrap',
        'speciesGentoo' = 'Gentoo', 
        'flipper_length_cm' = 'Flipper length (cm)')

modelplot(mod, coef_map = cm)
```

# Several models

The main `modelsummary` functions allows you to create a table with the results of several models side-by-side, by storing them in a (potentially named) list:

```{r, fig.height=3}
models <- list()
models[['Small model']] <- lm(culmen_length_cm ~ flipper_length_cm, data = dat)
models[['Medium model']] <- lm(culmen_length_cm ~ flipper_length_cm + body_mass_g, data = dat)
models[['Large model']] <- lm(culmen_length_cm ~ flipper_length_cm + body_mass_g + species, data = dat)

modelsummary(models, statistic = 'conf.int')
```

`modelplot` works the same way:

```{r, fig.height=2}
modelplot(models, coef_omit = 'Interc')
```

Instead of displaying results with "dodged" side-by-side lines, you can also use `facet`:

```{r, eval=FALSE, fig.height=2}
modelplot(models, facet = TRUE)
```


# Customizing your plots

The graphs produced by `modelplot` are simple `ggplot2` objects. You can thus post-process them using the normal suite of functions available for all objects of this type. Here, we change the axis labels, add a title and a caption, and use a color scheme inspired by Wes Anderson's *Darjeeling Limited*:

```{r, eval=TRUE, fig.height=3.5}
library(wesanderson)
library(ggplot2)

modelplot(models) +
    labs(x = 'Coefficients', 
         y = 'Term names',
         title = 'Linear regression models of "Culmen Length (cm)"',
         caption = "Data source: Gorman, Williams & Fraser (2014), packaged for R by @allison_horst") +
    scale_color_manual(values = wes_palette('Darjeeling1'))

  
```

In `ggplot2`, some visual choices must be made when calling the "geom", rather than with post-processing functions. For instance, the `size`, `color`, `fatten`, `linetype` arguments must all be specied inside the `geom_pointrange` function for them to take effect. `modelplot` will pass any unknown argument to `geom_pointrange`, so users can simply call:

```{r, fig.height=2}
modelplot(mod, size = 1, fatten = .7, color = 'darkgreen', linetype = 'dotted') + 
    theme_classic()
```

# Confidence intervals: change or omit

You can change the $\alpha$ level of your confidence intervals by changing the `conf_level` argument:

```{r, fig.height=2}
modelplot(mod, conf_level = .99)
modelplot(mod, conf_level = NULL)
```

# Raw data

If you would like to customize the plots even more than what `modelplot` allows, you can obtain the raw data used to draw the plots by setting `draw=FALSE`:

```{r, fig.height=2}
modelplot(models, draw = FALSE)
```
