---
title: '`modelplot`: Plot model coefficients with confidence intervals'
output:
  html_document: default
  pdf_document:
      latex_engine: xelatex
---

```{r, echo=FALSE, message=FALSE}
library(modelsummary)
library(tidyverse)
```

`modelplot` is a function from the `modelsummary` package. It allows you to plot model estimates and confidence intervals. It makes it easy to subset, rename, reorder, and customize plots using same mechanics as in `modelsummary`.

To illustrate how the function works, we fit a linear model to data about the [Palmer Penguins](https://github.com/allisonhorst/palmerpenguins):

```{r}
url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/palmerpenguins/penguins.csv'
dat <- read.csv(url)

# rescale mm -> cm
dat$bill_length_cm <- dat$bill_length_mm / 10
dat$flipper_length_cm <- dat$flipper_length_mm / 10

mod <- lm(bill_length_cm ~ flipper_length_cm + species, data = dat)
```

Then, we load the `modelsummary` library and call `modelplot`:

```{r, fig.height=2}
library(modelsummary)

modelplot(mod)
```

# Rename, reorder, subset

`modelplot` uses the same mechanics as `modelsummary` to rename, reorder, and subset estimates. First, you can use the `coef_omit` argument. This will omit any coefficient that matches a string or regular expression. To omit the intercept, for example, we can type:

```{r, fig.height=2}
modelplot(mod, coef_omit = 'Interc')
```

Second, you can use the `coef_map` argument. `coef_map` is a named character vector, where names correspond to the original term names, and values correspond the names you want to assign. Any variable that is *not* included in `coef_map` will be excluded. Variables will also be drawn in the same order as in `coef_map`:

```{r, fig.height=2}
cm <- c('speciesChinstrap' = 'Chinstrap',
        'speciesGentoo' = 'Gentoo', 
        'flipper_length_cm' = 'Flipper length (cm)')

modelplot(mod, coef_map = cm)
```

# Several models

The main `modelsummary` functions allows you to create a table with the results of several models side-by-side, by storing them in a (potentially named) list:

```{r, fig.height=3}
models <- list(
  "Small model" = lm(bill_length_cm ~ flipper_length_cm, data = dat),
  "Medium model" = lm(bill_length_cm ~ flipper_length_cm + body_mass_g, data = dat),
  "Large model" = lm(bill_length_cm ~ flipper_length_cm + body_mass_g + species, data = dat))

modelsummary(models, statistic = 'conf.int')
```

`modelplot` works the same way:

```{r, fig.height=2}
modelplot(models, coef_omit = 'Interc')
```

Instead of displaying results with "dodged" side-by-side lines, you can also use `facet`:

```{r, eval=FALSE, fig.height=2}
modelplot(models, facet = TRUE)
```

# Customizing plots

The graphs produced by `modelplot` are simple `ggplot2` objects. You can thus post-process them using the normal suite of functions available for all objects of this type. Here, we change the axis labels, add a title and a caption, and use a color scheme inspired by Wes Anderson's *Darjeeling Limited*:

```{r, eval=TRUE, fig.height=3.5}
library(wesanderson)
library(ggplot2)

modelplot(models) +
    labs(x = 'Coefficients', 
         y = 'Term names',
         title = 'Linear regression models of "Bill Length (cm)"',
         caption = "Data source: Gorman, Williams & Fraser (2014), packaged for R by @apreshill and @allison_horst") +
    scale_color_manual(values = wes_palette('Darjeeling1'))

  
```

In `ggplot2`, some visual choices must be made when calling the "geom", rather than with post-processing functions. For instance, the `size`, `color`, `fatten`, `linetype` arguments must all be specified inside the `geom_pointrange` function for them to take effect. `modelplot` will pass any unknown argument to `geom_pointrange`, so users can simply call:

```{r, fig.height=2}
modelplot(mod, size = 1, fatten = .7, color = 'darkgreen', linetype = 'dotted') + 
    theme_classic()
```

## Conditional colors and shape

Note: This section requires a version of `modelsummary` greater than 1.2.0 [or the development version.](https://github.com/vincentarelbundock/modelsummary#installation)

In a [very nice Stack Overflow answer](https://stackoverflow.com/a/74835661/342331), Allan Cameron shows how we can use the `aes()` function from `ggplot2` to add conditional aesthetics. For example, if we want to display statistically significant coefficients in a different color:

```{r}
#| fig.asp = .3
library(ggplot2)
mod <- lm(hp ~ factor(gear) + factor(cyl), data = mtcars)

modelplot(mod, coef_rename = TRUE) +
  aes(color = ifelse(p.value < 0.001, "Significant", "Not significant")) +
  scale_color_manual(values = c("grey", "black"))
```

## Example: Using facets to compare models

Customizing plots with `ggplot2` makes `modelplot` very flexible. For example, imagine you want to compare the coefficients of three models with different dependent variables. First, we load the packages and estimate our models:

```{r}
library(ggplot2)
library(modelsummary)

models <- list(
  lm(vs ~ carb + mpg + cyl, data = mtcars),
  lm(disp ~ carb + mpg + cyl, data = mtcars),
  lm(hp ~ carb + mpg + cyl, data = mtcars))
```

Then, we use the `dvnames` function to rename our list with names matching the the dependent variable in each model:

```{r}
models <- dvnames(models)
```

By calling `modelplot` with the `draw=FALSE` argument, we see the raw data used to draw the plot. Here, we see that there is a `model` column:

```{r}
modelplot(models, draw = FALSE)
```

Finally, we use the `model` column as our identifier in `ggplot2`’s `facet_grid` command to display models side by side:

```{r}
modelplot(models, color = "black") + facet_grid(~model)
```

# Confidence intervals: change or omit

You can change the $\alpha$ level of your confidence intervals by changing the `conf_level` argument:

```{r, fig.height=2}
modelplot(mod, conf_level = .99)
modelplot(mod, conf_level = NULL)
```

# Background annotations

Sometimes, you want to display annotations on a plot, but you would like to draw these annotations *behind* the `geom_pointrange` which displays the estimates. Since `modelplot` draws the `geom_pointrange` automatically, any `ggplot2` annotation you add to the plot using `+` will be added on *top* of the existing ones.

To add your annotations in the background, you can pass them as a list of `ggplot2` "geoms":

```{r}
library(ggplot2)

b <- list(geom_vline(xintercept = 0, color = 'orange'),
          annotate("rect", alpha = .1,
                   xmin = -.5, xmax = .5, 
                   ymin = -Inf, ymax = Inf),
          geom_point(aes(y = term, x = estimate), alpha = .3, 
                     size = 10, color = 'red'))

modelplot(mod, background = b)
```


# Raw data & More customization

If you would like to customize the plots even more than what `modelplot` allows, you can obtain the raw data used to draw the plots by setting `draw=FALSE`:

```{r, fig.height=2}
modelplot(models, draw = FALSE)
```

This allows users to use external tools such as [the powerful `ggdist` package](https://mjskay.github.io/ggdist/). In this example, we use the `purrr::map_dfr` function to call `modelplot` several times with different confidence levels. Then, we draw a plot where the different confidence intervals are drawn with different thicknesses:

```{r}
library(tidyverse)
library(modelsummary)
library(ggdist)

# fit
models <- list(
  lm(mpg ~ am, mtcars),
  lm(mpg ~ am + cyl, mtcars))

# summarize
dat <- map_dfr(c(.8, .9, .99), function(x) {
  modelplot(models, conf_level = x, draw = FALSE) %>%
  mutate(.width = x)
})

# plot
ggplot(dat, aes(
    y = term, x = estimate,
    xmin = conf.low, xmax = conf.high,
    color = model)) +
  ggdist::geom_pointinterval(
    position = "dodge",
    interval_size_range = c(1, 3),
    fatten_point = .1)
```
