---
title: "Multiple imputation"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*Warning:* The code in this vignette relies on `tidy` and `glance` methods which were recently added to the `mice` package. As of 2020-06-12, they were only available in the development version of the package (>3.9.0). The most recent version of `mice` can be installed by calling: `remotes::install_github('stefvanbuuren/mice')`

`modelsummary` can pool and display analyses on several datasets imputed using the `mice` or `Amelia` packages. This code illustrates how:

```{r, message=FALSE}
library(mice)
library(Amelia)
library(modelsummary)

# Download data from `Rdatasets`
url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/HistData/Guerry.csv'
dat <- read.csv(url)[, c('Clergy', 'Commerce', 'Literacy')]

# Insert missing values
dat$Clergy[sample(1:nrow(dat), 10)] <- NA
dat$Commerce[sample(1:nrow(dat), 10)] <- NA
dat$Literacy[sample(1:nrow(dat), 10)] <- NA

# Impute with `mice` and `Amelia`
dat_mice <- mice(dat, m = 5, printFlag = FALSE)
dat_amelia <- amelia(dat, m = 5, p2s = 0)$imputations

# Estimate models
mod <- list()
mod[['Listwise deletion']] <- lm(Clergy ~ Literacy + Commerce, dat)
mod[['Mice']] <- with(dat_mice, lm(Clergy ~ Literacy + Commerce)) 
mod[['Amelia']] <- lapply(dat_amelia, function(x) lm(Clergy ~ Literacy + Commerce, x))

# Pool results
mod[['Mice']] <- mice::pool(mod[['Mice']])
mod[['Amelia']] <- mice::pool(mod[['Amelia']])

# Summarize
modelsummary(mod)
```
