---
title: "Adding and customizing statistical models"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Supported models

`modelsummary` automatically supports all the models supported by the [broom package](broom.tidymodels.org). Specifically, `modelsummary` uses the `glance` and `tidy` methods from the `broom` package to extract information from model objects. To see if a package is supported out-of-the-box, load the `broom` package, and see if the `tidy` and `glance` methods produce valid output:

```{r, eval=FALSE}
library(broom)

tidy(mod)
glance(mod)
```

If the `tidy` and `glance` functions do not work on your model type, you may consider opening an issue on the Github website of the `broom` package: https://github.com/tidymodels/broom/issues

Note that several packages supply additional `tidy` and `glance` functions. Loading these packages can increase the range of models supported by `modelsummary`. For example, loading the [broom.mixed package](https://github.com/bbolker/broom.mixed) allows modelsummary to support a wide variety of mixed (hierarchical, multi-level) models (e.g., `lme4`, `brms`, `rstanarm`).

```{r, eval=FALSE}
library(broom.mixed)
library(modelsummary)

modelsummary(mod)
```

# Customizing existing models

The information that `modelsummary` can display about a model is determined by the output of the `broom::glance` and `broom::tidy` functions. `glance` is used the extract the information at the the bottom of the table, where goodness-of-fit measures are displayed. `tidy` is used to extract the information in the body of the table: parameter and uncertainty estimates.

Sometimes users will want to include information that is not supplied by those functions. A pretty easy way to include extra information is to define new `glance_custom` and `tidy_custom` methods. To illustrate, we estimate two linear regression models using the `lm` function:

```{r}
library(modelsummary)

mod <- list()
mod[[1]] <- lm(hp ~ mpg + drat, mtcars)
mod[[2]] <- lm(wt ~ mpg + drat + am, mtcars)
```

In `R`, the `lm` function produces models of class "lm":

```{r}
class(mod[[1]])
```

Let's say you would like to print the dependent variable for each model of this particular class. All you need to do is define a new method called `glance_custom.lm`. This method should return a data.frame (or tibble) with 1 row, and 1 column per piece of information you want to display. For example:

```{r}
glance_custom.lm <- function(x) {
    dv <- as.character(formula(x)[2])
    out <- tibble::tibble(`Dependent variable:` = dv)
    return(out)
}
```

;
ow, let's customize the body of the table. The `statistic_override` argument already allows users to customize uncertainty estimates. But imagine you want to override the *coefficient estimates* of your "lm" models. Easy! All you need to do is define a `tidy_custom.lm` method which returns a data.frame (or tibble) with one column called "term" and one column called "estimate".

Here, we'll substitute estimates by an up/down arrow which represents their signs:

```{r}
tidy_custom.lm <- function(x) {
    s <- summary(x)$coefficients
    out <- tibble::tibble(term = row.names(s),
                          estimate = ifelse(s[,1] > 0, 'тнб', 'тнг'))
    return(out)
}
```

After you define the `glance_custom` and `tidy_custom` methods, `modelsummary` will automatically display your customized model information:

```{r}
modelsummary(mod)
```

Note that you can define a `std.error` column in `tidy_custom.lm` to replace the uncertainty estimates instead of the coefficients.

## Fixed effects regression

One common use-case for `glance_custom` is to display the list of "fixed effects" included in a linear regression model.  

The `feols` function from the `fixest` package offers an extremely fast way to estimate fixed effects regression models. The `feols` function produces an object of class "fixest", which stores the fixed effects variables in a character vector called "fixef_vars". To display those fixed effects, we create a `glance_custom.fixest` and call `modelsummary`:

```{r}
glance_custom.fixest <- function(x) {
    out <- tibble::tibble(.rows = 1)
    for (n in x$fixef_vars) {
        out[[paste('FE: ', n)]] <- 'X'
    }
    return(out)
}

library(fixest)
library(modelsummary)

url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/plm/EmplUK.csv'
dat <- read.csv(url)
mod <- list()
mod[[1]] <- feols(emp ~ wage, dat)
mod[[2]] <- feols(emp ~ wage | firm, dat)
mod[[3]] <- feols(emp ~ wage | firm + year, dat)

modelsummary(mod)
```

# Adding new models

`modelsummary` relies on two functions from the `broom` package to extract model information: `tidy` and `glance`. If `broom` doesn't support the type of model you are trying to summarize, `modelsummary` won't support it out of the box. Thankfully, it is extremely easy to add support for most models using custom methods.

For example, models produced by the `MCMCglmm` package are not currently supported by `broom`. To add support, you simply need to create a `tidy` and a `glance` method:

```r
# load packages and data
library(modelsummary)
library(MCMCglmm)
data(PlodiaPO)

# add custom functions to extract estimates (tidy) and goodness-of-fit (glance) information
tidy.MCMCglmm <- function(object, ...) {
    s <- summary(object, ...)
    ret <- tibble::tibble(term = row.names(s$solutions),
                          estimate = s$solutions[, 1],
                          conf.low = s$solutions[, 2],
                          conf.high = s$solutions[, 3])
    ret
}
glance.MCMCglmm <- function(object, ...) {
    ret <- tibble::tibble(dic = object$DIC,
                          n = nrow(object$X))
    ret
}

# estimate a simple model
model <- MCMCglmm(PO ~ 1 + plate, random = ~ FSfamily, data = PlodiaPO, verbose=FALSE, pr=TRUE)

# summarize the model
modelsummary(model, statistic = 'conf.int')
```

Two important things to note. First, the methods are named `tidy.MCMCglmm` and `glance.MCMCglmm` because the model object I am trying to summarize is of class `MCMCglmm`. You can find the class of a model by running: `class(model)`.

Second, in the example above, we used the `statistic = 'conf.int'` argument. This is because the `tidy` method produces `conf.low` and `conf.high` columns. In most cases, users will define `std.error` column in their custom `tidy` methods, so the `statistic` argument will need to be adjusted.

If you create new `tidy` and `glance` methods, please consider contributing them to `broom` so that the rest of the community can benefit from your work: https://github.com/tidymodels/broom


# 2-stage instrumental variable estimation 

2-stage instrumental variable (IV) estimators are popular in many disciplines. Analysts often want to draw tables that include:

1. The 2nd stage estimates
2. The 1st stage estimates, but only for variables *not* included in the 2nd stage (i.e., the "instruments").

The problem is that many IV regression packages do not supply results for the 1st stage. Even when these results are accessible, the `tidy` methods supplied by `broom` only return the 2nd stage results.

To achieve our goal, we will:

1. Define a new `tidy.iv` method which extracts information about both stages of the IV estimation.
2. Change the class of our model objects to `iv`. This ensure that the new `tidy` method is triggered by `modelsummary`.
3. Sort the coefficients using the `coef_map` argument, to ensure that 1st stage results are displayed below 2nd stage results.

For convenience, `modelsummary` includes two unexported functions which can do most this for you. Reading [the annotated code for these two functions](https://github.com/vincentarelbundock/modelsummary/blob/master/R/convenience.R) could be an instructive exercise for those who wish to exploit everything that `modelsummary` has to offer.

To print IV regression results from `lfe::felm` models, we execute this code:

```{r, message=FALSE}
library(lfe)

models <- list(
  felm(wt ~ drat | 0 | (disp ~ hp), data = mtcars),
  felm(wt ~ drat + vs | 0 | (disp ~ hp), data = mtcars)
  )

# define a new method to combine tidy information about both stages
tidy.iv <- modelsummary:::tidy_felm_iv

# change the model classes to trigger the new method
class(models[[1]]) <- class(models[[2]]) <- c('iv', class(models[[1]]))

# use helper function to sort coefficients with 1st stage last
cm <- modelsummary:::coef_map_felm_iv(models)

modelsummary(models, coef_map=cm)
```
