---
title: "Adding and customizing statistical models"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Adding new models

`modelsummary` relies on two functions from the `broom` package to extract model information: `tidy` and `glance`. If `broom` doesn't support the type of model you are trying to summarize, `modelsummary` won't support it out of the box. Thankfully, it is extremely easy to add support for most models using custom methods.

For example, models produced by the `MCMCglmm` package are not currently supported by `broom`. To add support, you simply need to create a `tidy` and a `glance` method:

```r
# load packages and data
library(modelsummary)
library(MCMCglmm)
data(PlodiaPO)

# add custom functions to extract estimates (tidy) and goodness-of-fit (glance) information
tidy.MCMCglmm <- function(object, ...) {
    s <- summary(object, ...)
    ret <- tibble::tibble(term = row.names(s$solutions),
                          estimate = s$solutions[, 1],
                          conf.low = s$solutions[, 2],
                          conf.high = s$solutions[, 3])
    ret
}
glance.MCMCglmm <- function(object, ...) {
    ret <- tibble::tibble(dic = object$DIC,
                          n = nrow(object$X))
    ret
}

# estimate a simple model
model <- MCMCglmm(PO ~ 1 + plate, random = ~ FSfamily, data = PlodiaPO, verbose=FALSE, pr=TRUE)

# summarize the model
msummary(model, statistic = 'conf.int')
```

Two important things to note. First, the methods are named `tidy.MCMCglmm` and `glance.MCMCglmm` because the model object I am trying to summarize is of class `MCMCglmm`. You can find the class of a model by running: `class(model)`.

Second, in the example above, we used the `statistic = 'conf.int'` argument. This is because the `tidy` method produces `conf.low` and `conf.high` columns. In most cases, users will define `std.error` column in their custom `tidy` methods, so the `statistic` argument will need to be adjusted.

If you create new `tidy` and `glance` methods, please consider contributing them to `broom` so that the rest of the community can benefit from your work: https://github.com/tidymodels/broom

# Customizing existing models

The set of available statistics for any given model is determined by the output of the `broom::glance` function. Sometimes, you want to include information that is not included in `glance` output. For instance, you may want to display whether certain regression models include "fixed effects". 

One way to circumvent the limitations of glance is to create a custom method for your models. To illustrate, we load the `lfe` package, which provides the `felm` function to estimate linear regression models with fixed effects. Then, we simulate some data:

```{r, message=FALSE}
library(lfe)
library(broom)
library(modelsummary)

x <- rnorm(1000)
x2 <- rnorm(length(x))
id <- factor(sample(20,length(x),replace=TRUE))
firm <- factor(sample(13,length(x),replace=TRUE))
id.eff <- rnorm(nlevels(id))
firm.eff <- rnorm(nlevels(firm))
u <- rnorm(length(x))
y <- x + 0.5*x2 + id.eff[id] + firm.eff[firm] + u
```

The models produced by `felm` store the names of fixed effects in an object called "fe". For example, if `x` is your models, then `x$fe` will be a character vector with the names of all your fixed effects variables.

We create a custom `glance` method that extracts this information and returns it alongside the regular `glance` output:

```{r}
glance.felm_custom <- function(x, ...) {
    out <- broom:::glance.felm(x, ...)
    for (fe in names(x$fe)) {
        out[[paste('Fixed effects:', fe)]] <- 'X'
    }
    out
}
```

Then, we create a function to fit our models. This function passes all its arguments forward to `felm` using ellipses (`...`). Then, it assigns a new class name. This tells `modelsummary` that it should extract fixed effects names:

```{r}
felm_custom <- function(...) {
    out <- felm(...)
    class(out) <- c('felm_custom', class(out))
    out
}
```

Finally, we fit models and print the table:

```{r}
mod <- list()
mod[[1]] <- lm(y ~ x + x2)
mod[[2]] <- felm_custom(y ~ x + x2 | id)
mod[[3]] <- felm_custom(y ~ x + x2 | firm)
mod[[4]] <- felm_custom(y ~ x + x2 | id + firm)

msummary(mod)
```
