---
title: "Adding and customizing statistical models"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Customizing existing models

The information that `modelsummary` can display about a model is determined by the output of the `broom::glance` and `broom::tidy` functions. `glance` is used the extract the information at the the bottom of the table, where goodness-of-fit measures are displayed. `tidy` is used to extract the information in the body of the table: parameter and uncertainty estimates.

Sometimes users will want to include information that is not supplied by those functions. A pretty easy way to include extra information is to define new `glance_custom` and `tidy_custom` methods. To illustrate, we estimate two linear regression models using the `lm` function:

```{r}
library(modelsummary)

mod <- list()
mod[[1]] <- lm(hp ~ mpg + drat, mtcars)
mod[[2]] <- lm(wt ~ mpg + drat + am, mtcars)
```

In `R`, the `lm` function produces models of class "lm":

```{r}
class(mod[[1]])
```

Let's say you would like to print the dependent variable for each model of this particular class. All you need to do is define a new method called `glance_custom.lm`. This method should return a data.frame (or tibble) with 1 row, and 1 column per piece of information you want to display. For example:

```{r}
glance_custom.lm <- function(x) {
    dv <- as.character(formula(x)[2])
    out <- tibble::tibble(`Dependent variable:` = dv)
    return(out)
}
```

Now, let's customize the body of the table. The `statistic_override` argument already allows users to customize uncertainty estimates. But imagine you want to override the *coefficient estimates* of your "lm" models. Easy! All you need to do is define a `tidy_custom.lm` method which returns a data.frame (or tibble) with one column called "term" and one column called "estimate".

Here, we'll substitute estimates by an up/down arrow which represents their signs:

```{r}
tidy_custom.lm <- function(x) {
    s <- summary(x)$coefficients
    out <- tibble::tibble(term = row.names(s),
                          estimate = ifelse(s[,1] > 0, 'тнб', 'тнг'))
    return(out)
}
```

After you define the `glance_custom` and `tidy_custom` methods, `msummary` will automatically display your customized model information:

```{r}
msummary(mod)
```

Note that you can define a `std.error` column in `tidy_custom.lm` to replace the uncertainty estimates instead of the coefficients.

## Fixed effects regression

One common use-case for `glance_custom` is to display the list of "fixed effects" included in a linear regression model.  

The `feols` function from the `fixest` package offers an extremely fast way to estimate fixed effects regression models. The `feols` function produces an object of class "fixest", which stores the fixed effects variables in a character vector called "fixef_vars". To display those fixed effects, we create a `glance_custom.fixest` and call `msummary`:

```{r}
glance_custom.fixest <- function(x) {
    out <- tibble::tibble(.rows = 1)
    for (n in x$fixef_vars) {
        out[[paste('FE: ', n)]] <- 'X'
    }
    return(out)
}

library(fixest)
library(modelsummary)

url <- 'https://vincentarelbundock.github.io/Rdatasets/csv/plm/EmplUK.csv'
dat <- read.csv(url)
mod <- list()
mod[[1]] <- feols(emp ~ wage, dat)
mod[[2]] <- feols(emp ~ wage | firm, dat)
mod[[3]] <- feols(emp ~ wage | firm + year, dat)

msummary(mod)
```

# Adding new models

`modelsummary` relies on two functions from the `broom` package to extract model information: `tidy` and `glance`. If `broom` doesn't support the type of model you are trying to summarize, `modelsummary` won't support it out of the box. Thankfully, it is extremely easy to add support for most models using custom methods.

For example, models produced by the `MCMCglmm` package are not currently supported by `broom`. To add support, you simply need to create a `tidy` and a `glance` method:

```r
# load packages and data
library(modelsummary)
library(MCMCglmm)
data(PlodiaPO)

# add custom functions to extract estimates (tidy) and goodness-of-fit (glance) information
tidy.MCMCglmm <- function(object, ...) {
    s <- summary(object, ...)
    ret <- tibble::tibble(term = row.names(s$solutions),
                          estimate = s$solutions[, 1],
                          conf.low = s$solutions[, 2],
                          conf.high = s$solutions[, 3])
    ret
}
glance.MCMCglmm <- function(object, ...) {
    ret <- tibble::tibble(dic = object$DIC,
                          n = nrow(object$X))
    ret
}

# estimate a simple model
model <- MCMCglmm(PO ~ 1 + plate, random = ~ FSfamily, data = PlodiaPO, verbose=FALSE, pr=TRUE)

# summarize the model
msummary(model, statistic = 'conf.int')
```

Two important things to note. First, the methods are named `tidy.MCMCglmm` and `glance.MCMCglmm` because the model object I am trying to summarize is of class `MCMCglmm`. You can find the class of a model by running: `class(model)`.

Second, in the example above, we used the `statistic = 'conf.int'` argument. This is because the `tidy` method produces `conf.low` and `conf.high` columns. In most cases, users will define `std.error` column in their custom `tidy` methods, so the `statistic` argument will need to be adjusted.

If you create new `tidy` and `glance` methods, please consider contributing them to `broom` so that the rest of the community can benefit from your work: https://github.com/tidymodels/broom


