---
title: "Dynamic documents with `Rmarkdown` and `knitr`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(modelsummary)
```

## Dynamic documents: `Rmarkdown` and `knitr`

You can use `modelsummary` to insert tables into dynamic documents with `knitr` or `Rmarkdown`. Here is a working example Rmarkdown file which can be converted to HTML, PDF, or RTF using the `knitr` package. 

* [modelsummary_example.Rmd](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/modelsummary_example.Rmd)
    - [modelsummary_example.pdf](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/modelsummary_example.pdf)
    - [modelsummary_example.html](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/modelsummary_example.html)
    - [modelsummary_example.rtf](https://github.com/vincentarelbundock/modelsummary/blob/master/examples/modelsummary_example.rtf)

Open the `.Rmd` file in RStudio and click the "Knit" button. Note that for PDF output, you must include the `booktabs` package in your header (see the example file above).
