---
title: "`modelsummary` and `Rmarkdown`: Customizing the appearance of your tables"
output:
  rtf_document: default
  pdf_document: default
  html_document: default
---

This file illustrates how to use `modelsummary` to produce PDF, HTML, and RTF (Microsoft Word-compatible) files from a single Rmarkdown document. 

# A first table

To begin we estimate three linear regression models using the `mtcars` data. Then, we load the `modelsummary` package and call the `modelsummary` function:

```{r}
library(modelsummary)

models <- list()
models[[1]] <- lm(mpg ~ cyl, mtcars)
models[[2]] <- lm(mpg ~ cyl + drat, mtcars)
models[[3]] <- lm(hp ~ cyl + drat, mtcars)

modelsummary(models,
             title='Determinants of Car Features',
             statistic='conf.int')
```

Without any modification, this code will produce a nice table, whether the document is compiled to PDF, HTML, or RTF.^[The Rmarkdown output in the header must be set to either "pdf_document", "html_document", or "rtf_document".] In fact, tables produced using *any* of the `modelsummary` built-in options and arguments should compile correctly in all three formats.

One major benefit of `modelsummary` is that regression tables can be customized using the powerful `gt` and `kableExtra` libraries. To achieve this, we *post-process* the output of `modelsummary()` using functions from the `gt` or `kableExtra` packages. Achieving this in an Rmarkdown file requires some slight, but very easy, tweaks to our code. The next two sections explain what those tweaks are. 

# Output formats: `gt` vs. `kableExtra`

`modelsummary` supports several table-making packages: `gt`, `kableExtra`, `flextable`, `huxtable`. These packages are fantastic, but they each have (minor) disadvantages. For instance,

* `gt`'s LaTeX support is immature. As a result, producing PDF files from `Rmarkdown` using `gt` does not work yet.
* `kableExtra` does not support RTF output.

In the rest of this example file, we will demonstrate how to use `gt` and `kableExtra` functions to customize tables. However, we will not create tables using `gt` in PDF documents, and we will not create tables using `kableExtra` in RTF documents. To achieve this, we detect the Rmarkdown output format and create two boolean variables:

```{r}
is_rtf <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'rtf'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
```

In chunks with `gt` code, we set `eval=!is_latex`. In code chunks with `kableExtra` code, we set `eval=!is_rtf`.

# Customizing tables with `gt`

We can use functions from the `gt` package to post-process and customize a `modelsummary` table:

```{r, eval=!is_latex, fig.pos='!H'}
library(gt)

modelsummary(models, 
             output = 'gt',
             title = 'Table customized using `gt` functions.',
             stars = TRUE,
             notes = c('First custom note to contain text.',
                       'Second custom note with different content.')) %>%
   # spanning labels
   tab_spanner(label = 'Miles / Gallon', columns = 2:3) %>%
   tab_spanner(label = 'Horsepower', columns = 4) %>%
   # color
   tab_style(style = cell_text(color = "blue", weight = "bold"),
             locations = cells_body(columns = 1)) %>%
   tab_style(style = cell_fill(color = "pink"),
             locations = cells_body(rows = 3))
```

# Customizing tables with `kableExtra`

We can use functions from the `kableExtra` package to post-process and customize a `modelsummary` table. To do this, we load the `kableExtra` package, and we set `output='kableExtra'` in the `modelsummary()` call:

```{r, eval=!is_rtf, fig.pos='!H'}
library(kableExtra)

modelsummary(models,
             output = 'kableExtra',
             title = 'Table customized using `kableExtra` functions.',
             stars = TRUE,
             notes = c('First custom note to contain text.',
                       'Second custom note with different content.')) %>%
    # spanning labels
    add_header_above(c(" " = 1, "Miles / Gallon" = 2, "Horsepower" = 1)) %>%
    # color
    row_spec(3, background = 'pink') %>%
    column_spec(1, color = 'blue')
```
