---
title: "Using `modelsummary` in an Rmarkdown document"
output:
  html_document: default
  rtf_document: default
  pdf_document: default
header-includes:
- \usepackage{booktabs}
- \usepackage{xcolor}
---

This file illustrates how to use `modelsummary` to produce PDF, HTML, and RTF (Microsoft Word-compatible) files from a single Rmarkdown document. 

# Header

At the top of every Rmarkdown document, there is a "header" enclosed between two "---" lines, and written in YAML markup syntax. The first important thing to note is that in the current document, we have including the following code in the header:

```
header-includes:
- \usepackage{booktabs}
- \usepackage{xcolor}
```

These lines are required for PDF documents with `modelsummary` tables. Under the hood, Rmarkdown uses LaTeX to create PDF documents. All the tables produced by `modelsummary` require the LaTeX `booktabs` package. In addition, features like colors require loading additional LaTeX packages `xcolor`. The [`kableExtra` documentation](https://haozhu233.github.io/kableExtra/) explains which LaTeX packages may be required for different use cases.

# A first table

To begin we estimate three linear regression models using the `mtcars` data:

```{r}
library(modelsummary)
library(kableExtra)
library(gt)
models <- list()
models[[1]] <- lm(mpg ~ cyl, mtcars)
models[[2]] <- lm(mpg ~ cyl + drat, mtcars)
models[[3]] <- lm(hp ~ cyl + drat, mtcars)
```

Then, we load the `modelsummary` package and call the `msummary` function:

```{r}
msummary(models,
         title = 'Determinants of Car Features',
         statistic = 'conf.int')
```

Without any modification, this code will produce a nice table, whether the document is compiled to PDF, HTML, or RTF.^[The Rmarkdown output in the header must be set to either "pdf_document", "html_document", or "rtf_document".] In fact, tables produced using *any* of the `modelsummary` built-in options and arguments should compile correctly in all three formats.

One major benefit of `modelsummary` is that regression tables can be customized using the powerful `gt` and `kableExtra` libraries. To achieve this, we *post-process* the output of `msummary()` using functions from the `gt` or `kableExtra` packages. Achieving this in an Rmarkdown file requires some slight, but very easy, tweaks to our code. The next two sections explain what those tweaks are. 

# Output formats: `gt` vs. `kableExtra`

The two external packages that `modelsummary` uses to create tables are `gt` and `kableExtra`. These packages are fantastic, but they each have (minor) disadvantages. In particular,

* `gt`'s LaTeX support is not yet mature, and creating PDF files often breaks in Rmarkdown.
* `kableExtra` does not support RTF output.

In the rest of this example file, we will demonstrate how to use `gt` and `kableExtra` functions to customize tables. However, we will not create tables using `gt` in PDF documents, and we will not create tables using `kableExtra` in RTF documents. To achieve this, we detect the Rmarkdown output format and create two boolean variables:

```{r}
is_rtf <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'rtf'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'
```

In chunks with `gt` code, we set `eval=!is_latex`. In code chunks with `kableExtra` code, we set `eval=!is_rtf`.

# Customizing tables with `gt`

We can use functions from the `gt` package to post-process and customize a `modelsummary` table:^[The following code chunk is set to `eval=!is_latex`. It will not be executed when the Rmarkdown document is compiled to a PDF file.]

```{r, eval=!is_latex, fig.pos='!H'}
library(gt)

msummary(models,
         title = 'Table customized using `gt` functions.',
         stars = TRUE,
         notes = c('First custom note to contain text.',
                   'Second custom note with different content.')) %>%
   # spanning labels
   tab_spanner(label = 'Miles / Gallon', columns = 2:3) %>%
   tab_spanner(label = 'Horsepower', columns = 4) %>%
   # color
   tab_style(style = cell_text(color = "blue", weight = "bold"),
             locations = cells_body(columns = 1)) %>%
   tab_style(style = cell_fill(color = "pink"),
             locations = cells_body(rows = 3))
```

# Customizing tables with `kableExtra`

In `modelsummary`, the default output format for HTML tables is `gt`. If we want to use `kableExtra` functions to customize our HTML tables instead, we must declare our preference by setting the `modelsummary_html` option:

```{r}
library(kableExtra)

options(modelsummary_html = 'kableExtra')
```

We can use functions from the `kableExtra` package to post-process and customize a `modelsummary` table:^[The following code chunk is set to `eval=!is_rtf`. It will not be executed when the Rmarkdown document is compiled to an RTF file.]:

```{r, eval=!is_rtf, fig.pos='!H'}
msummary(models,
         title = 'Table customized using `kableExtra` functions.',
         stars = TRUE,
         notes = c('First custom note to contain text.',
                   'Second custom note with different content.')) %>%
    kable_styling %>%
    # spanning labels
    add_header_above(c(" " = 1, "Miles / Gallon" = 2, "Horsepower" = 1)) %>%
    # color
    row_spec(3, background = 'pink') %>%
    column_spec(1, color = 'blue')
```